Exploring Multi-Scale Spatiotemporal Twitter User Mobility Patterns with a Visual-Analytics Approach

### 2016-10-08 ijgi-148112-for proofreading/ijgi-148112-can be published.tex
profreading 2

% Authors, for the paper (add full first names)
\Author{Junjun Yin $^{1,3}$ and Zhenhong Du $^{2,3}$*}
% Authors, for metadata in PDF
\AuthorNames{Junjun Yin and Zhenhong Du}

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Department of Geography and Geographic Information Science, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA; jyn@illinois.edu\\
$^{2}$ \quad Institute of Geographic Information Science, School of Earth Sciences, Zhejiang University, Hangzhou, 310028, China; duzhenhong@zju.edu.cn\\
$^{3}$ \quad CyberGIS Center for Advanced Digital and Spatial Studies, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA}

% Contact information of the corresponding author
\corres{Correspondence: duzhenhong@zju.edu.cn; Tel.: +8613819192989}

@@

In this paper, we have employed a visual-analytics approach to exploring the Twitter user mobility patterns across multi-level spatial scales and temporal ranges in the continuous United States (i.e., excluding Alaska and Hawaii) during the year 2014.
The mobility data is extracted from over 1.3 billion geo-located Twitter messages (i.e., tweets) from January 1$^{st}$ to December 31$^{st}$, 2014 over North America with over 6 million Twitter users and over 1 TB in file size.
To address the data-intensive challenge embedded in this dataset, we have developed a scalable visual-analytics framework tailored to accommodate large volume of geo-located tweets.
This framework is implemented based on high-performance distributed computing environment using Apache Hadoop (http://hadoop.apache.org/), which is an open source software framework to enable distributed processing of large datasets across computing clusters.
Enabled by this framework, we have performed a set of statistical analysis to understand multi-scale spatiotemporal Twitter user mobility patterns. 
We have modeled the frequency of Twitter users visiting different locations to study the collective user visiting behaviors, where we have identified temporal similarities in the distributions.
In particular, Twitter user mobility patterns measured by user displacements and radius of gyrations of individuals~\cite{gonzalez2008understanding} have revealed different groups of Twitter users with multi-scale or multi-modal mobility patterns and multiple travel modes~\cite{Jurdak2015}.
By further studying such mobility patterns in different temporal ranges, we have identified both consistency and seasonal fluctuations regarding the distance decay effects in the corresponding mobility patterns.
In addition, our approach provides an interactive 3D virtual globe web mapping interface to enable exploratory geo-visual analytics for understanding the detailed Twitter user movement flows within a given spatial scale and time window.

@@

\section{Mobility patterns in Location Based Social Media data}
\subsection{Geo-located Twitter data for studying large-scale user movements}
To understand detailed mobility patterns of individuals, the capability to capture human movements with fine-grained spatial and temporal granularity is critical.
In this connection, using GPS trackers tends to produce, to date, the most accurate records of individuals' movements regarding the accuracy of recorded user locations and update frequency~\cite{zheng2008understanding}.
However, such data are often limited in spatial scale (e.g., within a specific city or region) from a small group of people, for example, 226 and 182 volunteers participated in collecting such mobility data in~\cite{rhee2011levy} and~\cite{zheng2010geolife} respectively.
Other than tracking people directly, the vehicle-based GPS traces are often tied to specific vehicles (e.g. taxi), which are only accessible for a certain group of people~\cite{kung2014exploring}.

@@

In this connection, it becomes increasingly popular for researchers to exploit the publicly accessible mobility data captured from today's pervasive Location Based Social Media (LBSM) platforms (e.g., Foursquare and Twitter).
LBSM enables users to attach their current location as a geo-tag to the message they post, which is derived from either the GPS or Wi-Fi positioning with a high position resolution down to 10 meters~\cite{Jurdak2015}.
A Big Data scenario emerges when millions social media users constantly post messages.
In this study, geo-located Twitter data are chosen as a source for studying detailed mobility patterns.
Compared to other LBSM platforms, Twitter is one of the most popular platforms and is been actively used in many countries.
It provides a publicly accessible streaming API (https://dev.twitter.com/streaming/overview) for easy data access.
Indeed, many other LBSM data can be collected from the data streams, such as Foursquare check-in data~\cite{cranshaw2012livehoods,hasan2013understanding}.

@@

\subsection{Data-intensive challenges for multi-scale geo-visual analytics}
Mobility data are essentially a collection of spatiotemporal records of people re-allocating across the geographic space.
To study mobility patterns of individuals, a space-time trajectory of each individual user should be modeled and constructed to quantify the collective movements over space and time.
Based on the extracted space-time trajectories, aforementioned studies are able to perform analysis, such as the measurements of user displacements and radius of gyrations of individuals, to study the mobility dynamics.
Indeed, space-time trajectory is one of the core concepts in H{\"a}gerstrand's time geography to understand the embedded spatiotemporal dynamics~\cite{hagerstrand1985time}, which has provided useful insights to explore movements across different geographical scales and temporal ranges.
For example, a geo-visualization approach was used to study human activity patterns, where user trajectories were mapped in a 3D space ordered by timestamps in the third dimension~\cite{kwan2004geovisualization}.
While such an approach enables visualization of individual trajectories, its capability is limited in dealing with large-volume movement datasets~\cite{andrienko2007designing}.
Instead of directly visualizing an individual user's trajectories, a space-time cube approach was proposed to analyzing and visualizing the collective trajectories.
It provides flexibilities in setting up both spatial scales and temporal ranges, and therefore is used to study mobility patterns across different spatial units (e.g., countries, states, and cities, etc.) and identify the changes over space and time~\cite{maceachren2001research, maceachren2004maps}.
In this regard, visual-analytics methods are proposed to better convey the findings in terms of analyzing and visualizing multi-level spatiotemporal mobility patterns~\cite{andrienko2007designing,andrienko2007visual}.
Visual-analytics methods focus on the synergy of computational and analytical methods to reduce the visual clutter, where aggregation methods are suggested to perform grouping/dividing individual's moving trajectories at different spatial and temporal granularity, e.g., utilizing the space-time cube approach~\cite{andrienko2007designing}.
Employing visual-analytics methods dealing with massive movement datasets is not only beneficial for optimizing visualizations but also provides a great deal of flexibilities for performing statistical analysis in seeking mobility patterns with different level of spatiotemporal details.

@@

\section{Materials and Methods}
\subsection{Geo-located Twitter data}
Geo-located tweets are tweets appended with an additional geo-tag in the form of a pair of geographical coordinates, which represents the location a tweet was sent at.
In this study, the geo-located tweets were downloaded using the Twitter Streaming API, where we specified a geographical bounding box as an area-of-interest to retrieve all the geo-located tweets that fall within it.
To ensure complete coverage over the continuous United States, we implemented a crawler that selects North America as the initial area-of-interest, where the geographical boundary is specified with lower left (latitude: 5.4, longitude: -167.3) and upper right (latitude: 83.2, longitude: -52.2).
The crawler is constantly running with over 2 million geo-located raw tweets ($\sim$2 GB in size) collected per day.
We have collected more than 1.3 billion geo-located tweets from January 1$^{st}$ to December 31$^{st}$, 2014 with 6,147,430 Twitter users and 1 TB in file size.
In particular, this data collection of the year 2014 was originally used to map the spatial spread of flu in North America during the time period~\cite{padmanabhan2014flumapper}.

As a social media account is not equal to a real person in the physical world~\cite{tsou2015}, to ensure the data quality, the collected raw tweets were further filtered by the following steps: We first removed duplicated messages (https://support.twitter.com/articles/18311-the-twitter-rules) in the dataset; and then we removed non-human users based on the heuristic of unusual relocating speed discussed in~\cite{hawelka2014geo,Jurdak2015}. 
In this case, we adopted the speed limit value as 240 m/s used in~\cite{Jurdak2015}, where we examined all the consecutive locations of each user and excluded those with relocating speed over the limit.
Note that the original location information embedded in each geo-located tweet is given in units of latitude and longitude, the distance is calculated by the great-circle distance between two points on a sphere with the haversine formula.
Finally, we used the geographic boundaries of the continuous United States (excluding Alaska and Hawaii) to further restrict the remaining tweets, where the technical details is presented in the following section. Based on these reinforcements, the dataset contains 1,052,861,000 tweets and 4,559,205 unique users.

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.55\linewidth]{./figures/Overall_Architecture222}
\caption{The overall system architecture of the framework}
\label{fig:overall_archi}
\end{figure}
\FloatBarrier

\subsection{Space-time Twitter user trajectories}
To derive meaningful mobility patterns of individuals, a space-time trajectory of each individual user should be constructed~\cite{hagerstrand1985time}.
Each raw geo-located tweet contains multiple fields of information, such as the created time, country, language code, and location, etc.
To construct a space-time trajectory from the data collection, we are interested in the following fields: \textit{user ID, location, timestamp}, which can be represented by a tuple $\left\langle id, loc, t\right\rangle$, where \textit{id} is a unique string representing a Twitter user's id; \textit{loc} is the recorded location of the message represented as a pair of projected coordinates $\left\langle x, y\right\rangle$;
and \textit{t} is the timestamp of when the message was posted; A Twitter user's space-time trajectory is defined as follows.
\newline

\noindent\emph{\textbf{Definition 1. Space-time Twitter user trajectory:}} The space-time trajectory of a Twitter user is defined as a collection of recorded geo-locations in the chronological order (i.e., based on the attached timestamp):
\newline

@@

To remove non-human users based on unusual relocating speed, a user will be removed if the speed between any two consecutive locations in the user's trajectory with $speed$ $(loc_{i} - loc_{i-1}) > 240 m/s $.
Based on this definition for modeling the space-time Twitter user trajectories, we converted the process of extracting trajectories from the raw geo-located Twitter data as a MapReduce task. Specifically, each mapper utilizes the unique user id as a key to prepares the records that belong to the same user and send them to a reducer. Once the reducers receive the $\langle key, value\rangle$ pairs, a Twitter user's space-time trajectory is formed by the sorting the locations in chronological order while considering the speed limit.
\newline

\noindent\emph{\textbf{Definition 2. Visitation behavior, displacement and radius of gyration:}} As each space-time Twitter user trajectory records all the locations a user has visited, the visitation behavior refers to the frequency of a user visiting different locations within a specific time frame.
This metric provides an overall assessment regarding the diversity and similarity in the collective mobility pattern~\cite{gao2012exploring}.

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.6\linewidth]{./figures/multilevel}
\caption{Hierarchical spatial layers for aggregating movements in different level-of-details}
\label{fig:multilevel}
\end{figure}
\FloatBarrier

\section{Multi-scale spatiotemporal Twitter user mobility patterns}
\subsection{Spatiotemporal Twitter user mobility patterns}
The situation of using geo-located tweets as proxies to infer people's movements is complex as users' tweeting behavior can be significantly different from one to another, in particular, the frequency and time-interval between two consecutive tweets.
For example, some people may tweet once a day while others do more; some people may tweet regularly while others do not.  
These tweeting behaviors are expected as such human dynamics are also seen in the mobile phone call data~\cite{gonzalez2008understanding}. 
Many studies have carried out data collection within a certain time period (e.g., a year in our case).
However, as the geo-located tweets were collected in a continuous fashion, it is necessary to examine the sensitivity regarding these behaviors to ensure we are not just capturing a random snapshot from the whole data streams.

@@

\begin{figure}[ht]
\centering
\includegraphics[width=1.0\linewidth]{./figures/visitation}
\caption{Two-tier power law distribution of the collective Twitter user visitation behaviors}
\label{fig:visitation}
\end{figure}
\FloatBarrier

@@

Figure~\ref{fig:displacement} (a) shows the probability distribution of the overall displacements, which is approximated by $P(d) \sim \lambda_{1} e^{-\lambda_{1}(d - d_{min})}, d_{min}=10~m$ from [10 m, 70 m] (accounting for 2 $\%$ of the population), $ P(d) \sim \beta\lambda_{1}d^{\beta-1}e^{-\lambda^{1}(d^\beta-d_{min}^\beta)}, d_{min}=100~m$ from [100 m, 80 km] (accounting for 93 $\%$ of the population), and $P(d) \sim {d}^{-\alpha}$ [$>$ 80 km] (accounting for 5 $\%$ of the population).
In addition, the displacement in the distance bound from 100 m and 80 km in Figure~\ref{fig:displacement} (b) can be further approximately by two power-law distributions with a cutting point at 5 km (53$\%$ distances are less than 5 km and 40$\%$ distances between 5 km and 80 km), which indicates two different travel modes, such as inter- or intra-city movements.
Overall, the fitting functions with different distance bounds suggest the existence of multi-scale or multi-modal mobility patterns~\cite{Jurdak2015} of the Twitter users in the continuous United States, for example, the displacements larger than 80 km could be related to inter-state travels and stronger distance decay effects are observed in longer distance travels.

The probability distribution of radius of gyrations of individuals at the national level (Figure~\ref{fig:gyration} (a)) is approximated by $P(r_{g}) \sim \lambda_{2} e^{-\lambda_{2}(r_{g} - {r_{g}}_{min})}, {r_{g}}_{min}=10~m$ from [10 m, 50 m], $P(r_{g}) \sim \lambda_{2} e^{-\lambda_{2}(r_{g} - {r_{g}}_{min})}$ from [50 m, 30 km], and $P(r_{g}) \sim {r_{g}}^{-\alpha}$ [$>$ 30 km].
In particular, the radius of gyration between 50 m and 30 km can be further approximately by two power law distributions with a cutting point at 6 km (Figure~\ref{fig:gyration} (b)), which suggest two main types of spatial coverage of from the collected Twitter users in the continuous United States.
The distribution shows that around $10\%$ the tweet population has a radius of gyration less than 50 meters, which indicates those twitter users mostly tweet at a particular place, such as home or office;  around 60$\%$ of the population has a radius of gyration less than 30 km, which indicates that most of the collected Twitter user movements are ``short'' distances, e.g., within a city locale. Note that the accuracy of these values for defining the distance bound depends on the accuracy of the location information of each geo-located tweet.

\begin{figure}[ht]
\centering
\includegraphics[width=1.0\linewidth]{./figures/displacement}
\caption{(a) The probability distribution of the collective Twitter user displacements P(d) (b) the distance between [100 m, 80 km] is approximated by a double power-law functions (c) The probability distribution of the accumulated displacements of individual Twitter users P(d) (d) The probability distribution of the accumulated displacements of individual Twitter users in 3 different months}
\label{fig:displacement}
\end{figure}
\FloatBarrier

We also measured the distribution of the radius of gyration of Twitter users at different spatial scales, specifically, the state and city level.
In this study, we selected the state Illinois and California for comparisons at the state level (Figure~\ref{fig:gyration} (c)), whereas we chose Chicago city as an example (Figure~\ref{fig:gyration} (d)) at the city level.
Interestingly but not surprisingly, the P($r_{g}$) at the state level can also be approximated by a combination of three functions: an exponential function, a stretched-exponential function and a power-law function.
We noticed that distance bound of the radius of gyration at the state level is at 10 km instead of 30 km at the national level.
The distance decay effects in larger spatial coverage [$>$ 30 km] slightly differ, in this case, the P($r_{g}$) decreases faster in smaller size state (i.e., Illinois) than the large size state (i.e., California).
In particular, the P($r_{g}$) over Chicago city can be fitted by similar functions.
However, as it reflects intra-city level mobility patterns, there is no distinct distance range to indicate large spatial coverage.

\begin{figure}[ht]
\centering
\includegraphics[width=1.0\linewidth]{./figures/gyration2}
\caption{ (a) The probability distribution of radius of gyration of individual Twitter users P($r_{g}$) at the national level (b) the distance between [50 m, 30 km] is approximated by a double power-law functions (c) P($r_{g}$) at the state level (Illinois and California) (d) P($r_{g}$) for Chicago city} 
\label{fig:gyration}
\end{figure}
\FloatBarrier

On the other hand, as our framework can aggregate Twitter user trajectories within different temporal ranges, we further analyzed the probability distributions of accumulated displacements took places in January, June, and October (Figure~\ref{fig:displacement} (d)) and radius of gyrations within 4 quarters in the year 2014 (Figure~\ref{fig:gyration_season}, in order to examine whether there are temporal changes in the mobility patterns.
While the probability distributions of accumulated displacements are almost identical in those selected three months,  we do find changes in the probability distributions of radius of gyrations in different quarters of the year. 
The fluctuations in the tails of the distributions indicate that long distance radius of gyrations (i.e., above 30 km) will experience more seasonal changes in the Twitter user mobility pattern, which means the increase or decrease of long distance movement activities in the corresponding time period. 
However, it is worthy noting that the overall trends in the Twitter user mobility patterns revealed by radius of gyrations are still consistent.

@@

\begin{figure}[ht]
\centering
\includegraphics[width=1.0\linewidth]{./figures/gyration_season}
\caption{The probability distribution of radius of gyration of individual Twitter users in different quarters of the year 2014}
\label{fig:gyration_season}
\end{figure}
\FloatBarrier

>>>>

% Authors, for the paper (add full first names)
\Author{Junjun Yin $^{1,3}$ and Zhenhong Du $^{2,3,*}$}
% Authors, for metadata in PDF
\AuthorNames{Junjun Yin and Zhenhong Du}

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Department of Geography and Geographic Information Science, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA; jyn@illinois.edu\\
$^{2}$ \quad Institute of Geographic Information Science, School of Earth Sciences, Zhejiang University, Hangzhou 310028, China; duzhenhong@zju.edu.cn\\
$^{3}$ \quad CyberGIS Center for Advanced Digital and Spatial Studies, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA}

% Contact information of the corresponding author
\corres{Correspondence: duzhenhong@zju.edu.cn; Tel.: +86-138-1919-2989}

@@

In this paper, we have employed a visual-analytics approach to exploring the Twitter user mobility patterns across multi-level spatial scales and temporal ranges in the continuous United States (i.e., excluding Alaska and Hawaii) during the year 2014.
The mobility data is extracted from over 1.3 billion geo-located Twitter messages (i.e., tweets) from 1st January to 31st December 2014 over North America with over 6 million Twitter users and over 1 TB in file size.
To address the data-intensive challenge embedded in this dataset, we have developed a scalable visual-analytics framework tailored to accommodate large volume of geo-located tweets.
This framework is implemented based on high-performance distributed computing environment using Apache Hadoop (http://hadoop.apache.org/), which is an open source software framework to enable distributed processing of large datasets across computing clusters.
Enabled by this framework, we have performed a set of statistical analysis to understand multi-scale spatiotemporal Twitter user mobility patterns. 
We have modeled the frequency of Twitter users visiting different locations to study the collective user visiting behaviors, where we have identified temporal similarities in the distributions.
In particular, Twitter user mobility patterns measured by user displacements and radius of gyrations of individuals~\cite{gonzalez2008understanding} have revealed different groups of Twitter users with multi-scale or multi-modal mobility patterns and multiple travel modes~\cite{Jurdak2015}.
By further studying such mobility patterns in different temporal ranges, we have identified both consistency and seasonal fluctuations regarding the distance decay effects in the corresponding mobility patterns.
In addition, our approach provides an interactive 3D virtual globe web mapping interface to enable exploratory geo-visual analytics for understanding the detailed Twitter user movement flows within a given spatial scale and time window.

@@

\section{Mobility Patterns in Location Based Social Media data}
\subsection{Geo-located Twitter Data for Studying Large-scale User Movements}
To understand detailed mobility patterns of individuals, the capability to capture human movements with fine-grained spatial and temporal granularity is critical.
In this connection, using GPS trackers tends to produce, to date, the most accurate records of individuals' movements regarding the accuracy of recorded user locations and update frequency~\cite{zheng2008understanding}.
However, such data are often limited in spatial scale (e.g., within a specific city or region) from a small group of people, for example, 226 and 182 volunteers participated in collecting such mobility data in~\cite{rhee2011levy} and~\cite{zheng2010geolife} respectively.
Other than tracking people directly, the vehicle-based GPS traces are often tied to specific vehicles (e.g. taxi), which are only accessible for a certain group of people~\cite{kung2014exploring}.

@@

In this connection, it becomes increasingly popular for researchers to exploit the publicly accessible mobility data captured from today's pervasive Location Based Social Media (LBSM) platforms (e.g., Foursquare and Twitter).
LBSM enables users to attach their current location as a geo-tag to the message they post, which is derived from either the GPS or Wi-Fi positioning with a high position resolution down to 10 meters~\cite{Jurdak2015}.
A Big Data scenario emerges when millions social media users constantly post messages.
In this study, geo-located Twitter data are chosen as a source for studying detailed mobility patterns.
Compared to other LBSM platforms, Twitter is one of the most popular platforms and is been actively used in many countries.
It provides a publicly accessible streaming API for easy data access~\cite{twitterAPI}.
Indeed, many other LBSM data can be collected from the data streams, such as Foursquare check-in data~\cite{cranshaw2012livehoods,hasan2013understanding}.

@@

\subsection{Data-intensive Challenges for Multi-scale Geo-visual Analytics}
Mobility data are essentially a collection of spatiotemporal records of people re-allocating across the geographic space.
To study mobility patterns of individuals, a space-time trajectory of each individual user should be modeled and constructed to quantify the collective movements over space and time.
Based on the extracted space-time trajectories, aforementioned studies are able to perform analysis, such as the measurements of user displacements and radius of gyrations of individuals, to study the mobility dynamics.
Indeed, space-time trajectory is one of the core concepts in H{\"a}gerstrand's time geography to understand the embedded spatiotemporal dynamics~\cite{hagerstrand1985time}, which has provided useful insights to explore movements across different geographical scales and temporal ranges.
For example, a geo-visualization approach was used to study human activity patterns, where user trajectories were mapped in a 3D space ordered by timestamps in the third dimension~\cite{kwan2004geovisualization}.
While such an approach enables visualization of individual trajectories, its capability is limited in dealing with large-volume movement datasets~\cite{andrienko2007designing}.
Instead of directly visualizing an individual user's trajectories, a space-time cube approach was proposed to analyzing and visualizing the collective trajectories.
It provides flexibilities in setting up both spatial scales and temporal ranges, and therefore is used to study mobility patterns across different spatial units (e.g., countries, states, and cities, etc.) and identify the changes over space and time~\cite{maceachren2001research, maceachren2004maps}.
In this regard, visual-analytics methods are proposed to better convey the findings in terms of analyzing and visualizing multi-level spatiotemporal mobility patterns~\cite{andrienko2007designing,andrienko2007visual}.
Visual-analytics methods focus on the synergy of computational and analytical methods to reduce the visual clutter, where aggregation methods are suggested to perform grouping/dividing individual's moving trajectories at different spatial and temporal granularity, e.g., utilizing the space-time cube approach~\cite{andrienko2007designing}.
Employing visual-analytics methods dealing with massive movement datasets is not only beneficial for optimizing visualizations but also provides a great deal of flexibilities for performing statistical analysis in seeking mobility patterns with different level of spatiotemporal details.

@@

\section{Materials and Methods}
\subsection{Geo-located Twitter Data}
Geo-located tweets are tweets appended with an additional geo-tag in the form of a pair of geographical coordinates, which represents the location a tweet was sent at.
In this study, the geo-located tweets were downloaded using the Twitter Streaming API, where we specified a geographical bounding box as an area-of-interest to retrieve all the geo-located tweets that fall within it.
To ensure complete coverage over the continuous United States, we implemented a crawler that selects North America as the initial area-of-interest, where the geographical boundary is specified with lower left (latitude: 5.4, longitude: -167.3) and upper right (latitude: 83.2, longitude: -52.2).
The crawler is constantly running with over 2 million geo-located raw tweets ($\sim$2 GB in size) collected per day.
We have collected more than 1.3 billion geo-located tweets from 1 January to 31 December 2014 with 6,147,430 Twitter users and 1 TB in file size.

In particular, this data collection of the year 2014 was originally used to map the spatial spread of flu in North America during the time period~\cite{padmanabhan2014flumapper}.
As a social media account is not equal to a real person in the physical world~\cite{tsou2015}, to ensure the data quality, the collected raw tweets were further filtered by the following steps: We first removed duplicated messages in the dataset~\cite{black2012twitter}; and then we removed non-human users based on the heuristic of unusual relocating speed discussed in~\cite{hawelka2014geo,Jurdak2015}.
In this case, we adopted the speed limit value as 240 m/s used in~\cite{Jurdak2015}, where we examined all the consecutive locations of each user and excluded those with relocating speed over the limit.
Note that the original location information embedded in each geo-located tweet is given in units of latitude and longitude, the distance is calculated by the great-circle distance between two points on a sphere with the haversine formula.
Finally, we used the geographic boundaries of the continuous United States (excluding Alaska and Hawaii) to further restrict the remaining tweets, where the technical details is presented in the following section. Based on these reinforcements, the dataset contains 1,052,861,000 tweets and 4,559,205 unique users.

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.55\linewidth]{./figures/Overall_Architecture222}
\caption{The overall system architecture of the framework.}
\label{fig:overall_archi}
\end{figure}
\FloatBarrier

\subsection{Space-time Twitter User Trajectories}
To derive meaningful mobility patterns of individuals, a space-time trajectory of each individual user should be constructed~\cite{hagerstrand1985time}.
Each raw geo-located tweet contains multiple fields of information, such as the created time, country, language code, and location, etc.
To construct a space-time trajectory from the data collection, we are interested in the following fields: \textit{user ID, location, timestamp}, which can be represented by a tuple $\left\langle id, loc, t\right\rangle$, where \textit{id} is a unique string representing a Twitter user's id; \textit{loc} is the recorded location of the message represented as a pair of projected coordinates $\left\langle x, y\right\rangle$;
and \textit{t} is the timestamp of when the message was posted; A Twitter user's space-time trajectory is defined as follows.
\newline

\noindent\textbf{Definition 1. Space-time Twitter user trajectory:} \emph{The space-time trajectory of a Twitter user is defined as a collection of recorded geo-locations in the chronological order (i.e., based on the attached timestamp):} 
\newline

@@

To remove non-human users based on unusual relocating speed, a user will be removed if the speed between any two consecutive locations in the user's trajectory with $speed$ $(loc_{i} - loc_{i-1}) > $ 240 m/s.
Based on this definition for modeling the space-time Twitter user trajectories, we converted the process of extracting trajectories from the raw geo-located Twitter data as a MapReduce task. Specifically, each mapper utilizes the unique user id as a key to prepares the records that belong to the same user and send them to reducer. Once the reducers receive the $\langle key, value\rangle$ pairs, a Twitter user's space-time trajectory is formed by the sorting the locations in chronological order while considering the speed limit.
\newline

\noindent\textbf{Definition 2. visitation behavior, displacement and radius of gyration:} \emph{As each space-time Twitter user trajectory records all the locations a user has visited, the visitation behavior refers the frequency of a user visiting different locations within a specific time frame.
This metric provides an overall assessment regarding the diversity and similarity in the collective mobility pattern}~\cite{gao2012exploring}.

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.6\linewidth]{./figures/multilevel}
\caption{Hierarchical spatial layers for aggregating movements in different level-of-details.}
\label{fig:multilevel}
\end{figure}
\FloatBarrier

\section{Multi-scale Spatiotemporal Twitter User Mobility Patterns}
\subsection{Spatiotemporal Twitter User Mobility Patterns}
The situation of using geo-located tweets as proxies to infer people's movements is complex as users' tweeting behavior can be significantly different from one to another, in particular, the frequency and time-interval between two consecutive tweets.
For example, some people may tweet once a day while others do more; some people may tweet regularly while others do not.  
These tweeting behaviors are expected as such human dynamics are also seen in the mobile phone call data~\cite{gonzalez2008understanding}. 
Many studies have carried out data collection within a certain time period (e.g., a year in our case).
However, as the geo-located tweets were collected in a continuous fashion, it is necessary to examine the sensitivity regarding these behaviors to ensure we are not just capturing a random snapshot from the whole data streams.

@@

\begin{figure}[ht]
\centering
\includegraphics[width=1.0\linewidth]{./figures/visitation}
\caption{Two-tier power law distribution of the collective Twitter user visitation behaviors.}
\label{fig:visitation}
\end{figure}
\FloatBarrier

@@

Figure~\ref{fig:displacement}a shows the probability distribution of the overall displacements, which is approximated by $P(d) \sim \lambda_{1} e^{-\lambda_{1}(d - d_{min})}, d_{min}=10~m$ from [10 m, 70 m] (accounting for 2 $\%$ of the population), $ P(d) \sim \beta\lambda_{1}d^{\beta-1}e^{-\lambda^{1}(d^\beta-d_{min}^\beta)}, d_{min}=100~m$ from [100 m, 80 km] (accounting for 93 $\%$ of the population), and $P(d) \sim {d}^{-\alpha}$ [$>$ 80 km] (accounting for 5 $\%$ of the population).
In addition, the displacement in the distance bound from 100 m and 80 km in Figure~\ref{fig:displacement}b can be further approximately by two power-law distributions with a cutting point at 5 km (53$\%$ distances are less than 5 km and 40$\%$ distances between 5 km and 80 km), which indicates two different travel modes, such as inter- or intra-city movements.
Overall, the fitting functions with different distance bounds suggest the existence of multi-scale or multi-modal mobility patterns~\cite{Jurdak2015} of the Twitter users in the continuous United States, for example, the displacements larger than 80 km could be related to inter-state travels and stronger distance decay effects are observed in longer distance travels.

The probability distribution of radius of gyrations of individuals at the national level (Figure~\ref{fig:gyration}a) is approximated by $P(r_{g}) \sim \lambda_{2} e^{-\lambda_{2}(r_{g} - {r_{g}}_{min})}, {r_{g}}_{min}=10~m$ from [10 m, 50 m], $P(r_{g}) \sim \lambda_{2} e^{-\lambda_{2}(r_{g} - {r_{g}}_{min})}$ from [50 m, 30 km], and $P(r_{g}) \sim {r_{g}}^{-\alpha}$ [$>$ 30 km].
In particular, the radius of gyration between 50 m and 30 km can be further approximately by two power law distributions with a cutting point at 6 km (Figure~\ref{fig:gyration}b), which suggest two main types of spatial coverage of from the collected Twitter users in the continuous United States.
The distribution shows that around $10\%$ the tweet population has a radius of gyration less than 50 meters, which indicates those twitter users mostly tweet at a particular place, such as home or office;  around 60$\%$ of the population has a radius of gyration less than 30 km, which indicates that most of the collected Twitter user movements are ``short'' distances, e.g., within a city locale. Note that the accuracy of these values for defining the distance bound depends on the accuracy of the location information of each geo-located tweet.

\begin{figure}[ht]
\centering
\includegraphics[width=1.0\linewidth]{./figures/displacement}
\caption{({\bf a}) The probability distribution of the collective Twitter user displacements P(d); ({\bf b}) the distance between [100 m, 80 km] is approximated by a double power-law functions; ({\bf c}) The probability distribution of the accumulated displacements of individual Twitter users P(d); ({\bf d}) The probability distribution of the accumulated displacements of individual Twitter users in 3 different months.}

\label{fig:displacement}
\end{figure}
\FloatBarrier

We also measured the distribution of the radius of gyration of Twitter users at different spatial scales, specifically, the state and city level.
In this study, we selected the state Illinois and California for comparisons at the state level (Figure~\ref{fig:gyration}c), whereas we chose Chicago city as an example (Figure~\ref{fig:gyration}d) at the city level.
Interestingly but not surprisingly, the P($r_{g}$) at the state level can also be approximated by a combination of three functions: an exponential function, a stretched-exponential function and a power-law function.
We noticed that distance bound of the radius of gyration at the state level is at 10 km instead of 30 km at the national level.
The distance decay effects in larger spatial coverage [$>$ 30 km] slightly differ, in this case, the P($r_{g}$) decreases faster in smaller size state (i.e., Illinois) than the large size state (i.e., California).
In particular, the P($r_{g}$) over Chicago city can be fitted by similar functions.
However, as it reflects intra-city level mobility patterns, there is no distinct distance range to indicate large spatial coverage.

\begin{figure}[ht]
\centering
\includegraphics[width=1.0\linewidth]{./figures/gyration2}
\caption{ ({\bf a}) The probability distribution of radius of gyration of individual Twitter users P($r_{g}$) at the national level; ({\bf b}) the distance between [50 m, 30 km] is approximated by a double power-law functions; ({\bf c}) P($r_{g}$) at the state level (Illinois and California); ({\bf d}) P($r_{g}$) for Chicago city.} 
\label{fig:gyration}
\end{figure}
\FloatBarrier

On the other hand, as our framework can aggregate Twitter user trajectories within different temporal ranges, we further analyzed the probability distributions of accumulated displacements took places in January, June, and October (Figure~\ref{fig:displacement}d) and radius of gyrations within 4 quarters in the year 2014 (Figure~\ref{fig:gyration_season}, in order to examine whether there are temporal changes in the mobility patterns.
While the probability distributions of accumulated displacements are almost identical in those selected three months,  we do find changes in the probability distributions of radius of gyrations in different quarters of the year. 
The fluctuations in the tails of the distributions indicate that long distance radius of gyrations (i.e., above 30 km) will experience more seasonal changes in the Twitter user mobility pattern, which means the increase or decrease of long distance movement activities in the corresponding time period. 
However, it is worthy noting that the overall trends in the Twitter user mobility patterns revealed by radius of gyrations are still consistent.

@@

\begin{figure}[ht]
\centering
\includegraphics[width=1.0\linewidth]{./figures/gyration_season}
\caption{The probability distribution of radius of gyration of individual Twitter users in different quarters of the year 2014.}
\label{fig:gyration_season}
\end{figure}
\FloatBarrier

The above analysis of Twitter user mobility patterns mainly focuses on the spatiotemporal aspects.
Our framework provides the flexibility to aggregate and extract Twitter user trajectories in a specific spatial scale and re-produce the analysis.
In particular, as it is evident from the above analysis that there are multi-scale or multi-modal Twitter user mobility patterns, this framework can help further look into the mobility pattern regarding how Twitter users move across different spatial scales and temporal ranges, which is measured by the movement flows between these spatial units.
The movement flows are obtained by aggregating the movements that started from and ended in the corresponding spatial units within the giving time frame.
In this case, we demonstrate the inter-state mobility patterns by using the framework to capture the movement flows between the states.
Note that the movement flows can be summarized across all the 10 spatial layers in the framework.
We tested the overall distribution of the movement flows (in the form of weighted in-degree and out-degree of a graph, where each state is treated as a node) among different states in the year 2014.
We found that the probability distribution of Twitter user movement flows of visiting different states follows a log-normal distribution: $p(x)\sim \frac{1}{x}exp[-\frac{(lnx - \mu)^{2}}{2\sigma^{2}}]$, which suggests the flux of Twitter user movements among the states are highly skewed and dominated by a few states (Figure~\ref{fig:state_flow}).
It indicates that the Twitter population is not proportional to account the movement flux between the states, which may provide some insights for other researchers in studying social-economical aspects of the migration dynamics.

\begin{figure}[ht]
\centering
\includegraphics[width=0.8\linewidth]{./figures/degree}
\caption{The distribution of Twitter user movement flows among different states in the year 2014 measured in weighted in- and out-degrees.}
\label{fig:state_flow}
\end{figure}
\FloatBarrier
